---
title: "Pa4"
subtitle: "This is getting harder!"
author: "Michele Goldin"
date: "2018/3/1"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r, load_libraries, message=FALSE, warning=FALSE}

library(untidydata)
library(xaringan)
library(plot3D)
library(tidyverse)

```

```{r, load data and explore}
fricatives <- read.csv('../data_raw/fricatives/fricatives.csv', header = TRUE, sep = ',')

str(fricatives)
head(fricatives)

```

---

#Descriptives

```{r, descriptives}

mean(fricatives$s_cog)
sd(fricatives$s_cog)
mean(fricatives$sh_cog)
sd(fricatives$sh_cog)
mean(fricatives$s_skewness)
sd(fricatives$s_skewness)
mean(fricatives$sh_skewness)
sd(fricatives$sh_skewness)
```

---

#Boxplot cog ~ phoneme

```{r, plot 1}

fricatives%>%
  select('s_cog', 'sh_cog')%>%
  gather(., key = cog, val = cogvalue)%>%
  separate(., col = cog, into = c('phoneme', 'cog'), sep="_")%>%
  ggplot(., aes(x=cogvalue, y = phoneme)) +
  geom_boxplot()
```

---

#Plot skewness ~ phoneme

```{r, plot 2}

fricatives%>%
  select('s_skewness', 'sh_skewness')%>%
  gather(., key = skewness, val = skewvalue)%>%
  separate(., col = skewness, into = c('phoneme2', 'skewness'), sep="_")%>%
  ggplot(., aes(x=skewvalue, y = phoneme2)) +
  geom_point()
```

---

#Boxplot cog ~ skewness of S

```{r, plot 3}

myfrics <- fricatives%>%
  gather(., 's_cog', 'sh_cog', key = cog, val = cogvalue)%>%
  separate(., col = cog, into = c('phoneme', 'cog'), sep="_")%>%
  gather(., 's_skewness', 'sh_skewness', key = skewness, val = skewvalue)%>%
  separate(., col = skewness, into = c('phoneme2', 'skewness'), sep="_")%>%
  filter(., phoneme2 == 's')

myfrics%>%
  ggplot(., aes(x = cogvalue, y = skewvalue)) +
  geom_boxplot()
```

---

#Make a table

##Mean and SD of COG

```{r, table_cog}
myfrics %>% 
  group_by(., cog, skewness) %>% 
  summarize(., mean_cog = mean(cogvalue), sd_cog = sd(cogvalue)) %>% 
  knitr::kable(., format = 'html', digits = 2)
```

##Mean and SD of Skewness

```{r, table_skewness}
myfrics %>% 
  group_by(., skewness) %>% 
  summarize(., mean_skewness = mean(skewvalue), sd_skewness = sd(skewvalue)) %>% 
  knitr::kable(., format = 'html', digits = 2)

```


---

#Scatterplot

```{r, plot 4}

myfrics%>%
  ggplot(., aes(x = cogvalue, y = skewvalue)) +
  geom_point()
```

---

#Model Summary

```{r, model summary}

  my_mod <- lm(cogvalue ~ skewvalue, data = myfrics)
summary(my_mod)
```

---

#Description

The mean cog of phoneme 's' is 5690.524, SD = 913.25 and the mean cog of phoneme 'sh' is 3994.823, SD = 697.09. The mean skewness of phoneme 's' is -0.7714211, SD = 0.28 and the mean skewness of phoneme 'sh' is 0.5527295, SD = 0.44. The scatterplot shows us that center of gravity as a function of 's' skewness. There is a positive correlation, as the center of gravity of both 's' and 'sh' phonemes increases, so does the skewness of 's' (B = 2664.3, SE = 526.7, t value = 5.06, p<.01).

---

#The end