---
title: "Pa4"
subtitle: "This is getting harder!"
author: "Michele Goldin"
date: "2018/3/1"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r, load_libraries, message=FALSE, warning=FALSE}

library(untidydata)
library(xaringan)
library(plot3D)
library(tidyverse)

```

```{r, load data and explore}
fricatives <- read.csv('../data_raw/fricatives/fricatives.csv', header = TRUE, sep = ',')

str(fricatives)
head(fricatives)

```

---

#Tidy Data

```{r, tidy_data}
myfrics <- fricatives %>%
  gather(., key = measurement, val = value, -obs) %>%
  separate(., col = measurement, into = c('phoneme', 'measurement'), sep="_") %>%
  spread(., key = measurement, value = value)

head(myfrics)
```

---

#Descriptives

```{r, descriptives, fig.width=8, fig.height=4}

mean(fricatives$s_cog)
sd(fricatives$s_cog)
mean(fricatives$sh_cog)
sd(fricatives$sh_cog)
mean(fricatives$s_skewness)
sd(fricatives$s_skewness)
mean(fricatives$sh_skewness)
sd(fricatives$sh_skewness)
```

---

#Make a table

##Mean and SD of COG and Skewness

```{r, table_cog, fig.width=8, fig.height=4}
myfrics %>% 
  group_by(., phoneme) %>% 
  summarize(., mean_cog = mean(cog), sd_cog = sd(cog), mean_skewness = mean(skewness), sd_skewness = sd(skewness)) %>% 
  knitr::kable(., format = 'html', digits = 2)
```

---

#Boxplot cog ~ phoneme

```{r, plot 1, fig.width=8, fig.height=4}

myfrics%>%
  ggplot(., aes(x=cog, y = phoneme)) +
  geom_boxplot()
```

---

#Plot skewness ~ phoneme

```{r, plot 2, fig.width=8, fig.height=4}

myfrics %>%
  ggplot(., aes(x=skewness, y = phoneme)) +
  geom_point()

```

---

#Boxplot cog ~ skewness of S

```{r, plot 3, fig.width=8, fig.height=4}

myfrics%>%
  filter(., phoneme == 's')%>%
  ggplot(., aes(x = cog, y = skewness)) +
  geom_point()

```


---

#Scatterplot

```{r, plot 4, fig.width=8, fig.height=4}

myfrics%>%
  ggplot(., aes(x = cog, y = skewness, color = phoneme)) +
  geom_point()

```

---

#Model Summary

```{r, model summary}

  my_mod <- lm(cog ~ skewness, data = myfrics)
summary(my_mod)

```

---

#Description

The mean cog of phoneme 's' is 5690.52, SD = 913.25 and the mean cog of phoneme 'sh' is 3994.82, SD = 697.09. The mean skewness of phoneme 's' is -0.77, SD = 0.28 and the mean skewness of phoneme 'sh' is 0.55, SD = 0.44. The first scatterplot shows us the center of gravity as a function of 's' skewness and the second plot shows center of gravity as a function of skewness of both 's' and 'sh' phonemes. There is a positive correlation, as the center of gravity of both 's' and 'sh' phonemes increases, so does the skewness of those phonemes (B = -544.5, SE = 233.3, t value = -2.33, p<.02).

---

#The end